workshop

### 2022-09-19 scripts/workshop/workshop.Rmd
update workshop

```{r}
species_comp <- data %>% group_by(Species) %>% summarize(mean = mean(SQMean),
                                                         var = var(SQMean),
                                                         se = sqrt(var(SQMean)/n()))

species_comp %>% ggplot(.,aes(x=Species, y=mean)) + geom_point() + geom_linerange(aes(ymin=mean-se,ymax=mean+se))
```

>>>>

### comparing ranked means with and without log-transformation of raw data

```{r}
vl <- readRDS(here("processed_data","vl.rds"))

supp1_raw <- vl %>% arrange(mean) %>% 
  mutate(abb_name = factor(abb_name, levels = abb_name)) %>% 
  ggplot(.,aes(x=abb_name,y=mean)) +
  geom_point() + 
  xlab("Species") + ylab("Viral Load") + 
  geom_linerange(aes(ymin=mean-se,ymax=mean+se)) +
  geom_hline(yintercept = 1) + 
  labs(title = "Viral Loads") + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  scale_y_continuous(breaks=seq(0,6,1))

supp1_log10 <- vl %>% arrange(mean) %>% 
  mutate(abb_name = factor(abb_name, levels = abb_name)) %>% 
  ggplot(.,aes(x=abb_name,y=log1p_mean)) +
  geom_point() + 
  xlab("Species") + ylab("log1p(Viral Load)") + 
  geom_linerange(aes(ymin=log1p_mean-log1p_se,ymax=log1p_mean+log1p_se)) +
  geom_hline(yintercept = 1) + 
  labs(title = "Viral Loads") + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  scale_y_continuous(breaks=seq(0,6,1))

supp1_raw
supp1_log10
```
